\section*{Experiences}
\begin{itemize}

    \item[] 
    \begin{tabular*}{0.95\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{Solution Engineer} & Since September 2022 \\
      \textit{\small Siemens AG} &  {\small \textit{Huizingen, Belgium}}\\
    \end{tabular*}
    \begin{itemize}
      \item Integrate SCADA EMS/ADMS (Energy Management System/ Advanced Distribution Management System) solutions, Siemens Spectrum Power 7, for energy transporters/distributors.
      \item Navigate Red Hat Enterprise Linux servers and Oracle databases in order to solve various issues.
      \item Provide training to customer on Siemens Spectrum Power 7. 
      \item Write a migration script to import data from an external system to Siemens Spectrum Power 7.
    \end{itemize}
    \item[] 
    \begin{tabular*}{0.95\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{Co-Founder/CTO} & November 2019 - September 2022 \\
      \textit{\small Work and Meet} &  {\small \textit{Mont-Saint-Guibert, Belgium}}\\
    \end{tabular*}
    \begin{itemize}
      \item Developped a marketplace platform from scratch : frontend, backend, databases, server, domain name, certificates, payment method.
      \item Met with clients to adapt the platform to their needs.
      \item Handled web development interns ; assigning tasks as scrum master, reviewing pull requests, merging branches, etc
    \end{itemize}
    \item[] 
    \begin{tabular*}{0.95\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{Project Intern} & September 2021 -- June 202 \\
      \textit{\small Uniwan} &  {\small \textit{Charleroi, Belgium}}\\
    \end{tabular*}
    \begin{itemize}
      \item Automated monitoring and management of remote MikroTik firewalls.
      \item Secured communications between the firewalls and monitoring/management server through VPN tunnels.
      \item Used Nagios XI to monitor a fleet of firewalls.
    \end{itemize}

    \item[] 
    \begin{tabular*}{0.95\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{Full-stack Web Developer} & July 2020 -- August 2020 \\
      \textit{\small BTI Belgium} &  {\small \textit{Fontaine-l'Évêque, Belgium}}\\
    \end{tabular*}
    \begin{itemize}
      \item Developed a front-end (HTML/Javascript) and back-end (PHP/SQL) using modern frameworks for an online marketplace aimed at local businesses.
      \item Taught interns and colleagues how to effectively use said frameworks, Angular and Laravel, as well as version control with Github.
      \item Documented all the code and the DevOps processes.
    \end{itemize}

\end{itemize}

